Towards Comparable Active Learning

### 2023-05-24 doc/al_benchmark_paper.tex
paper update

\title{Towards Comparable Active Learning}
\author{%
	David S.~Hippocampus\thanks{Use footnote for providing further information
		about author (webpage, alternative address)---\emph{not} for acknowledging
		funding agencies.} \\
	Department of Computer Science\\
	Cranberry-Lemon University\\
	Pittsburgh, PA 15213 \\
	\texttt{hippo@cs.cranberry-lemon.edu} \\
	% examples of more authors
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \AND
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
{\color{red} Version: Braindump}\\
Many different algorithms have been proposed for active learning. 
In this work we focus on those approaches that have shown consistent results over the years as well as newer approaches that have demonstrated significant lifts in their initial experiments.
AL algorithms can be categorized into two classes: Geometric approaches and uncertainty-based approaches.
Geometric approaches include CoreSet \cite{sener2017active} and TypiClust \cite{hacohen2022active}, which use clustering techniques to partition the data and then sample their unlabeled points based on the clusters.
Uncertainty-based approaches include classic uncertainty sampling (based on Shannon-Entropy and the margin-score), BALD \cite{kirsch2019batchbald} and BADGE \cite{ashdeep}, which use metrics to measure the classifiers state. \\ [1mm]
%
Some previous work also aimed to provide a benchmark suite for active learning:
The authors of \cite{beck2021effective} and \cite{li2022empirical} both focus on active learning in the image domain.
While \cite{beck2021effective} discuss a new metric to measure AL performance, which they call "Label Efficiency" and provide experiments on many common configurations for data preparation, model training and other hyperparameters, \cite{li2022empirical} focuses on combined approaches of AL and semi-supervised learning to aid model training.
The authors of \cite{hu2021towards} study models that are learned with AL techniques in the image and text domain.
They test for several different properties of the models including robustness, response to compression techniques and final performance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
Table \ref{tab:benchmark_comparison} shows a feature comparison between our proposed benchmark and several existing benchmarks in the literature, as well as methodological AL papers with an extensive experiments section. \\
{\color{red} TODO} We include in this table any methodological paper that experiments on at least two domains.
\begin{table}[h]
	\centering
	\begin{tabular}{l | c c c c c}
		Paper & Sampling & \# Datasets & Domains & Algorithms & Oracle \\
		\hline
		Beck et al. \cite{beck2021effective} & batch & 4 & 1 & 7 & - \\
		Hu et al. \cite{hu2021towards} & batch & 5 & 2 & 13 & - \\
		Li et al. \cite{li2022empirical} & batch & 5 & 1 & 13 & - \\
		Zhou et al. \cite{zhou2021towards} & batch & 3 & 2 & 2 & \checkmark \\
		\textbf{Ours} & single & 9 & 4 & 6 & \checkmark 
	\end{tabular}
	\caption{Comparison of our benchmark with the existing literature}
	\label{tab:benchmark_comparison}
\end{table}

@@

>>>>

\title{Towards Comparable Active Learning}
\author{%
	Thorben Werner 
	\thanks{Information Systems and Machine Learning Lab (ISMLL)} 
	\\
	Institute of Computer Science\\
	University of Hildesheim\\
	Universitätsplatz 1, 31141 Hildesheim \\
	\texttt{werner@ismll.de} \\
	% examples of more authors
	\And
	Johannes Burchert$^*$ \\
	Institute of Computer Science\\
	University of Hildesheim\\
	Universitätsplatz 1, 31141 Hildesheim \\
	\texttt{burchert@ismll.de} \\
	\AND
	Prof. Lars Schmidt-Thieme$^*$ \\
	Institute of Computer Science\\
	University of Hildesheim\\
	Universitätsplatz 1, 31141 Hildesheim \\
	\texttt{schmidt-thieme@ismll.uni-hildesheim.de} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
We constrain our work on pool-based active learning where a pool of unlabeled samples is fixed at the start of each experiment and samples are chosen sequentially.
Specifically, we are not experimenting on so-called batch active learning, where at each iteration multiple unlabeled samples are chosen at the same time.
Even though batch AL is the more active research domain, it does not have a principled advantage over single-sample AL except speed of computation.
Not only is the problem of optimizing a portfolio of unlabeled samples more complicated to solve, the algorithms also have systematically less information per sample to work with.
For this reason we propose to focus more research effort on single-sample AL to find better algorithms in an environment that is simpler to solve and easier to control.
Table \ref{tab:benchmark_comparison} shows a feature comparison between our proposed benchmark and several existing benchmarks in the literature, as well as methodological AL papers with experiments on at least two data domains.
\begin{table}[h]
	\centering
	\begin{tabular}{l | c c c c c}
		Paper & Sampling & \# Datasets & Domains & Algorithms & Oracle \\
		\hline
		Beck et al. \cite{beck2021effective} & batch & 4 & 1 & 7 & - \\
		Hu et al. \cite{hu2021towards} & batch & 5 & 2 & 13 & - \\
		Li et al. \cite{li2022empirical} & batch & 5 & 1 & 13 & - \\
		Zhou et al. \cite{zhou2021towards} & batch & 3 & 2 & 2 & \checkmark \\
		\textbf{Ours} & single & 9 & 4 & 6 & \checkmark 
	\end{tabular}
	\caption{Comparison of our benchmark with the existing literature}
	\label{tab:benchmark_comparison}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
{\color{red} Version: Braindump}\\
Many different algorithms have been proposed for active learning. 
In this work we focus on those approaches that have shown consistent results over the years as well as newer approaches that have demonstrated significant lifts in their initial experiments.
AL algorithms can be categorized into two classes: Geometric approaches and uncertainty-based approaches.
Geometric approaches include CoreSet \cite{sener2017active} and TypiClust \cite{hacohen2022active}, which use clustering techniques to partition the data and then sample their unlabeled points based on the clusters.
Uncertainty-based approaches include classic uncertainty sampling (based on Shannon-Entropy and the margin-score), BALD \cite{kirsch2019batchbald} and BADGE \cite{ashdeep}, which use metrics to measure the classifiers state. \\ [1mm]
%
Some previous work also aimed to provide a benchmark suite for active learning:
The authors of \cite{beck2021effective} and \cite{li2022empirical} both focus on active learning in the image domain.
While \cite{beck2021effective} discuss a new metric to measure AL performance, which they call "Label Efficiency" and provide experiments on many common configurations for data preparation, model training and other hyperparameters, \cite{li2022empirical} focuses on combined approaches of AL and semi-supervised learning to aid model training.
The authors of \cite{hu2021towards} study models that are learned with AL techniques in the image and text domain.
They test for several different properties of the models including robustness, response to compression techniques and final performance.
